Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2016-01-22 paper.tex
Re-insert Oxford commas
Fix up wake profiles figure caption

 \caption{Mean velocity field at $x/D=1$, $\lambda=1.9$ and $Re_D=1.0 \times
 10^6$.}

@@

 \caption{Turbulence kinetic energy at $x/D=1$, $\lambda=1.9$ and $Re_D=1.0
 \times 10^6$.}

@@

 \caption{Mean streamwise velocity \hl {(left)} and turbulence kinetic energy
 (right) profiles at $z/H=0.0$. The legend indicates $Re_D$.}
 %please use (a) and (b) to instead left and right and mark (a) and (b) in the figure.
 \label{fig:profiles}
\end{figure}

>>>>

 \caption{Mean velocity field at $x/D=1$, $\lambda=1.9$, and $Re_D=1.0 \times
 10^6$.}

@@

 \caption{Turbulence kinetic energy at $x/D=1$, $\lambda=1.9$, and $Re_D=1.0
 \times 10^6$.}

@@

     \caption{Mean streamwise velocity \textbf{(a)} and turbulence kinetic
         energy \textbf{(b)} profiles at $z/H=0.0$. Turbine diameter Reynolds number
         $Re_D$ is indicated by the legend.}

    \label{fig:profiles}
\end{figure}
